Summary Tables

### 2019-05-20 summary_tables.Rmd
add yll per hundred thousand by age outcome

  td1 <- df1 %>% filter(mmet == 0) %>% 
    summarise(perct_zeros = round(n() / nrow(df1) * 100, 1))

@@

  td4 <- df2 %>% gather(key = "scenario", value = "mmet") %>% 
    filter(mmet == 0) %>% 
    group_by(scenario) %>% 
    summarise(perct_zeros = round(n() / nrow(df2) * 100, 1))

>>>>

  td1 <- df1 %>% filter(mmet == 0) %>% 
    summarise(perct_zeros = round(dplyr::n() / nrow(df1) * 100, 1))

@@

  td4 <- df2 %>% gather(key = "scenario", value = "mmet") %>% 
    filter(mmet == 0) %>% 
    group_by(scenario) %>% 
    summarise(perct_zeros = round(dplyr::n() / nrow(df2) * 100, 1))
